%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[black]{banking}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[black]{banking}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.9, top=2cm]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Divyanshu}
\familyname{Jain}
%\title{Divyanshu Jain}               % optional, remove the line if not wanted
\address{3454 Jasmine Avenue Los Angeles}{California}    % optional, remove the line if not wanted
\mobile{(310) 500 9665}                    % optional, remove the line if not wanted
%% \phone{phone (optional)}                      % optional, remove the line if not wanted
%% \fax{fax (optional)}                          % optional, remove the line if not wanted
\email{divyanshu.jain@gmail.com}                      % optional, remove the line if not wanted
%% \homepage{www.eggwall.com}                % optional, remove the line if not wanted
%% \extrainfo{additional information (optional)} % optional, remove the line if not wanted
%%\photo[64pt]{mugshot}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%% \quote{Improve users' lives}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\vspace*{-12mm}
\maketitle
\vspace*{-8mm}
\section{Industry Experience}
\cventry{2008--present}{Member of Technical Staff}{Mojix Inc.}{Los Angeles}{}{ %Firmware Development for RFID Readers
\begin{itemize}%
\item Developed firmware for Mojix RFID Interrogators (implement real time protocol standardized by EPC to query and manage tag population). This involved coding in C for the Texas Instruments C64x series of DSP. 
\item Wrote microcontroller (ARM Cortex-M3) code in C for Mojix low power signal distributors and regenerators. 
\item Implemented a conductive testing procedure to characterize performance of RFID Readers via BER curves by simulating random tag signal mixed with Gaussian noise at different Eb/No values.
\item Coded a Java daemon to monitor the health of various components used in the Mojix network topology.
\item Member of the team involved in designing and implementing a proprietary protocol to transmit protocol commands and receive sensor data, tag data over a wired link passing through multiple devices in a massive distributed network.
\item Coded and developed a part of the  python - Tk based GUI to control, test and setup various parameters of our RFID system.
\end{itemize}}

\cventry{2008--2008}{Interim Engineering Intern}{Qualcomm Inc.}{San Diego}{}{ %Improved Google's Payment Fraud detection system
\begin{itemize}%
\item Wrote a high level design document for carrier frequency offset estimation for the LTE project and assembly coded the critical sections to optimize processor cycle usage.
\item Plotted the system timeline using GTK wave analyzer showing interaction between functions (channel estimation, frequency estimation, IFFT) and the respective time taken in each routine.  
\end{itemize}}

\section{Technical skills}
\cvcomputer{Languages}{C/C++, Python, Java}{Assembly}{TI TMS320C6000, ARM Cortex-M3}
\cvcomputer{Software}{MATLAB, Simulink, Office}{Platform}{Linux, Windows}
\cvcomputer{Concepts}{Signal Processing,  Filters, Probability,\newline Artificial Intelligence, Algorithms}{Hardware}{Pattern and Waveform Generators,\newline Oscilloscopes, Spectrum Analyzers}

\section{Education}
\cventry{2006--2007}{Masters in Electrical Engineering, GPA 3.7/4.0}{University of California}{Los Angeles, California}{}{}
\cventry{2002--2006}{Bachelors in Electrical Engineering, Aggregate 80.2/100.0}{Madhav Institute of Technology and Science}{Gwalior, India}{}{}


\section{Masters thesis}
\cvline{Title}{\emph{Optimization techniques for Implementing Real Time MIMO channel estimation on a DSP (TI-C64x)}}
\begin{itemize}%
\item Simulated minimum number of channel coefficient bits (quantization level) required to be within permissible error bounds.
\item Optimized hand written assembly code via novel techniques:
	\begin{itemize}%
	\item Leveraged input data properties. (Used simulated number of bits for division algorithm selection)
	\item Equalized load across different functional units of the processor. (by using alternate or suboptimal instructions)
	\item Eliminated cross path stalling by manual scheduling.
	\end{itemize}
\item Further optimized the assembly using conventional techniques of loop unrolling and software pipelining.
\end{itemize}

%\section{Awards}
%\cventry{June 2005}{Bhojwani scholarship for securing highest marks in junior year.}{Academic Distinction}{M.I.T.S. Gwalior, India}{}{}

%\section{Publications}
% Publications from a BibTeX file without multibib\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% for BibTeX numerical labels
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{dj_pub}       % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\nocitebook{book1,book2}
\bibliography{publications}   % 'publications' is the name of a BibTeX file
\bibliographystyle{plain}
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications_dj}   % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template_en.tex'.
